Social Visual Analytics: DevOps for Data Scientists

### 2015-03-23 system.tex
better distinguish colors; comment; capitalize GitHub

Figure~\ref{fig:something} shows the RCloud developer interface.
The center panel is a notebook for code and visualizations.
Code is edited in this panel, and visualizations are rendered.
An inventory of supplementary ``asset'' files, that are part of
the notebook, though not in its executable flow, are edited on the right.
Controls at the top of the screen allow the user to run, view, and
share the notebook. The result of code execution is the final cell of
the notebook.  On the left is a browsing area for searching and viewing
other users' notebooks, and a help system.

@@

To implement this, we built RCloud on top of Github's \emph{gists}~\cite{Github:2014:GG}.
Github offers a HTTP interface for creating simplified git repositories, the main limitation
being a restriction to text-only files in a single directory. The GitHub web-service
API provides most of the semantics we need for the versioning portion of the storage back end:
access to previous versions, comments, starring, and forking.

>>>>

Figure~\ref{fig:something} shows the RCloud developer interface.  The center
panel is a notebook for code and visualizations.  Code is edited in this panel,
and visualizations are rendered.  An inventory of supplementary ``asset'' files,
that are part of the notebook, though not in its executable flow, are edited on
the right.  Controls at the top of the screen allow the user to run, view, and
share the notebook. \gordon{Why are we talking about the callable interface
here?} The result of code execution is the final cell of the notebook.  On the
left is a browsing area for searching and viewing other users' notebooks, and a
help system.

@@

To implement this, we built RCloud on top of GitHub's \emph{gists}~\cite{GitHub:2014:GG}.
GitHub offers a HTTP interface for creating simplified git repositories, the main limitation
being a restriction to text-only files in a single directory. The GitHub web-service
API provides most of the semantics we need for the versioning portion of the storage back end:
access to previous versions, comments, starring, and forking.
